---
title: 'Staffing at Long Term Care Facilities Comparison: Beechtree, Cayuga Ridge, Kendall, Oak
  Hill; Ithaca, NY'
output:
  html_document: 
    keep_md: yes
  html_notebook: default
---


```{r setup, include=FALSE, warning=FALSE, echo=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load lbraries, message=FALSE, warning=FALSE, echo=FALSE}
# load libraries

library(tidyverse)
library(lubridate)
library(stringr)
library(webshot)

```


```{r load data, echo=FALSE, message=FALSE, warning=FALSE}

df_newyork <- read_rds("data/newyork_2018.rds")

df_ithaca <- df_newyork %>%
  filter(workdate >"2018-03-31",
         workdate < "2018-07-01") %>%
  filter(str_detect(provname, "BEECHTREE|CAYUGA RIDGE|KENDAL AT ITHACA|OAK HILL"))


```


## CNA staffing at long term care facilities, by day of week, Apr - Jun 2018


```{r, echo=FALSE, fig.height=5, fig.width=11, warning=FALSE}


ggplot(data = df_ithaca) +
  geom_path(mapping = aes(x = workdate, y = residents_per_cna, col = str_trunc(provname, 10) ), size = 0.3 ) +
  geom_point(mapping = aes(x = workdate, y = residents_per_cna, col = str_trunc(provname, 10)), size = 1.5) +
  labs(x = "",
       y = "Residents per CNA",
       title = "Staffing at Long Term Care Facilities, Ithaca NY",
       subtitle = "Residents per CNA by day, April - June 2018" ) +
  theme(legend.title = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  facet_grid(.~day) +
  scale_y_continuous(limits = c(7, 19), breaks = seq(8,18, by = 2))


```


```{r}

ggsave(filename = "output/ithaca_cna_staffing_pbj_2018_apr-jun_rmd.png",
       width=11,
       height=7,
       dpi = 600)


```

## Nursing Home Compare

https://www.medicare.gov/NursingHomeCompare/


The Medicare.Gov website contains profiles of facilities. (The comparison tool permits only 3 at a time.)


```{r, echo=TRUE, warning=FALSE, cache=TRUE}

webshot("https://www.medicare.gov/NursingHomeCompare/compare.html#cmprTab=0&cmprID=335017%2C335249%2C335793&cmprDist=1.5%2C2.4%2C4.3&lat=42.435511&lng=-76.5257007&loc=14850",
        "data/compare_seta_1.png",
        delay = 1.0)

```


## Beechtree Center for Rehabilitation and Nursing - ownership

Some of the information is inaccurate. The people listed as a managing employees no longer work at Beechtree.  

```{r, cache=TRUE, echo=FALSE, warning=FALSE}

webshot("https://www.medicare.gov/nursinghomecompare/ownership-info.html?ID=335017",
        "data/ownership_beechtree.png",
        delay = 1.0)
```


## Cayuga Ridge Extended Care - ownership

Why is ownership information unavailable for Cayuga Ridge?

```{r, cache=TRUE, echo=FALSE, warning=FALSE}

webshot("https://www.medicare.gov/nursinghomecompare/ownership-info.html?ID=335249",
        "data/ownership_cayugaridge.png",
        delay = 1.0)

```

## Kendall at Ithaca - ownership

```{r, cache=TRUE, echo=FALSE, warning=FALSE}

webshot("https://www.medicare.gov/nursinghomecompare/ownership-info.html?ID=335793",
        "data/ownership_kendall.png",
        delay = 1.0)

```


## Oak Hill Manor Nursing Home - ownership

```{r, cache=TRUE, echo=FALSE, warning=FALSE}


webshot("https://www.medicare.gov/nursinghomecompare/ownership-info.html?ID=335225",
        "data/ownership_oakhill.png",
        delay = 1.0)

```



